Molecular transport in human pial perivasculature

### 2024-03-11 paper/main.tex
Add some more references and summary of context.
Former-commit-id: 42cf4fc6a21e981afbbbea9f9c120c77f42b3755

\begin{itemize}
\item Vinje et al~\cite{vinje2021brain} and references therein illustrates the location and characteristics of human pial perivascular spaces.
\item Mestre et al~\cite{mestre2022periarteriolar} study the properties of pial perivascular spaces in detail in mice.
\item Mestre et al~\cite{mestre2018flow} measure and characterize pial perivascular transport and estimate flow magnitudes (in mice).
\item Bollman et al~\cite{bollmann2022imaging} image the human pial vasculature at high resolution (7T).
\item Hornkjøl et al~\cite{hornkjol2022csf} model CSF flow and solute transport in the human SAS and brain parenchyma. 
\item Mardal et al~\cite{mardal2022mathematical} give a succinct introduction to MRI-based computational brain modelling. 
\end{itemize}

>>>>

\begin{itemize}
\item Vinje et al~\cite{vinje2021brain} and references therein illustrates the location and characteristics of human pial perivascular spaces.
\item Mestre et al~\cite{mestre2022periarteriolar} study the properties of pial perivascular spaces in detail in mice.
\item Mestre et al~\cite{mestre2018flow} measure and characterize pial perivascular transport and estimate flow magnitudes (in mice).
\item
  Weller and coauthors conducted pioneering studies of perivascular spaces, flow and transport~\cite{zhang1990interrelationships, zhang1992directional}. They identified thin sheaths of pial cells surrounding arteries and arterioles (but not veins or venules) on the brain surface and within the human brain itself~\cite{zhang1990interrelationships}. Further, they observed that tracers spread along perivascular (arterial, venous and capillar) spaces in (rat) grey matter, and in the subarachnoid space (to the cribriform plate and nasal lymphatics)..   
\item In a series of papers, Bakker and coauthors study perivascular anatomy and solute transport~\cite{bedussi2017paravascular, bedussi2018paravascular}. They find that the subarachnoid space, the cisterns, ventricles and penetrating periarteriolar spaces form a continuous cerebrospinal-fluid filled space surrounding and penetrating the rat brain\cite{bedussi2017paravascular}. Moreover, they demonstrate pulsatile and directional (antegrade) flow in perivascular (predominantly periarterial) spaces on the brain surface.
\item Bollman et al~\cite{bollmann2022imaging} image the human pial vasculature at high resolution (7T).
\item Hornkjøl et al~\cite{hornkjol2022csf} model CSF flow and solute transport in the human SAS and brain parenchyma. 
\item Mardal et al~\cite{mardal2022mathematical} give a succinct introduction to MRI-based computational brain modelling. 
\end{itemize}
